Paper Consumption in Finland, 1488-1828

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

# Add indicator field: Turku or Not Turku
myplace <- "Turku"
df$myplace <- rep(NA, nrow(df))
df$myplace[df$publication_place == myplace] <- myplace
df$myplace[!df$publication_place == myplace & df$country == "Finland"] <- "Finland"
df$myplace[!df$publication_place == myplace & !df$country == "Finland"] <- "Foreign"
df$myplace <- factor(df$myplace, levels = rev(c("Other", "Finland", "Turku")))

@@

#p <- ggplot(dfs, aes(x = publication_decade, y = paper, color = myplace)) +
#     geom_point() + geom_smooth() +
#     ylim(0, max(dfs$paper)) +
#     ggtitle("Turku vs. other publication places")

@@

p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity") +
     ggtitle("Title count") +
     scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     xlab("Publication decade") + ylab("Title count (n)")
print(p)
```

>>>>

# Add indicator field: Turku or Not Turku
myplace <- "Turku"
df$myplace <- rep(NA, nrow(df))
df$myplace[df$publication_place == myplace] <- myplace
df$myplace[!df$publication_place == myplace & df$country == "Finland"] <- "Finland"
df$myplace[!df$country == "Finland"] <- "Foreign"
df$myplace <- factor(df$myplace, levels = rev(c("Foreign", "Finland", "Turku")))

@@

@@

p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity") +
     ggtitle("Title count") +
     scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     xlab("Publication decade") + ylab("Title count (n)")
print(p)

#p + guides(fill = guide_legend(order = 1))

```
